Co-citations in context

### 2019-05-15 cocit_r.tex
template and tex files for QSS

\articletype{Perspective}

@@

\begin{document}
\title[Shortened Version of Title]{Title of Article}
\subtitle{Subtitle Here}

@@

\author[Author Names]
{Author Names with affiliations\affil{1},
Another Name\affil{2}, Still another Name\affil{2},\\
\and Final Name\affil{1}}

\affiliation{1}{Department, Institution, City, Country}

@@

\affiliation{2}{Another Department, Institution, City, Country}

@@

\correspondingauthor{Author Name}{Corresponding author email address}

@@

\keywords{(a series of uncapitalized words, separated with commas)}

@@

\begin{abstract}
Abstract text here.
\end{abstract}

\begin{authorsummary}
Author summary here. 
\end{authorsummary}

\section{Sample Section}
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.
Text here. Text here. Text here. Text here.

@@

\bibliography{NETNbibsamp}

>>>>

\articletype{Research Article}

@@

\begin{document}
\title[Co-citations in context]{Co-citations in context}
\subtitle{Disciplinary heterogeneity is relevant}

@@

\author[Author Names]
{James Bradley\affil{1},
Sitaram Devarakonda\affil{2}, Avon Davey\affil{2}, Dmitriy Korobskiy\affil{2}, Siyu Liu\affil{2}, Tandy Warnow\affil{3}
\and George Chacko\affil{2}}

\affiliation{1}{Raymond A. Mason School of Business, College of William and Mary, Williamsburg, VA, USA}
\affiliation{2}{Netelabs, NET ESolutions Corporation, McLean, VA 22102, USA}
\affiliation{3}{Department of Computer Science, University of Illinois Urbana-Champaign, Champaign, IL 61820, USA}

@@

%\affiliation{2}{Another Department, Institution, City, Country}

@@

\correspondingauthor{George Chacko}{netelabs@nete.com}

@@

\keywords{(bibliometrics, co-citation analysis, random graphs )}

@@

\begin{abstract}
Citation analysis of the scientific literature has been used to study and define disciplinary boundaries, to trace the dissemination of knowledge, and to estimate impact. Co-citation, the frequency with which pairs of publications are cited, provides insight into how documents relate to each other and across fields. Co-citation analysis has been used to characterize combinations of prior work as conventional or innovative and to derive features of highly cited publications. Given the organization of science into disciplines, a key question is the sensitivity of such analyses to frame of reference. Our study examines this question using  semantically-themed citation networks. We observe that trends reported to be true across the scientific literature do not hold for focused citation networks, and conclude that co-citation analysis requires a contextual perspective.
\end{abstract}

% \begin{authorsummary} 
% \end{authorsummary}

\section{Introduction}
Citation and network analysis of  scientific literature reveals information on semantic relationships between publications, collaboration between scientists, and the practice of citation itself~\cite{de_solla_price_networks_1965,newman_structure_2001}. Co-citation, the frequency with which two documents are cited together in other documents~\cite{small_co-citation_1973,marshakova-shaikevich_co-citation_1973}, provides additional insights, including the identification of semantically related documents and fields. Uzzi et al. applied co-citation analysis to 17.9 million publications from the Web of Science (WoS) to identify novel combinations of prior research and to characterize highly cited papers. They analyzed co-citations of references (and journals) within publications, and computed a `z-score' for each journal pair using Monte Carlo simulations based on a random graph model. The set of journal-pair z-scores for each publication was  used to assess  conventionality and novelty, resulting in four categories: high or low conventionality (HC or LC) and high or low novelty (HN or LN), and all four combinations are possible. The authors concluded that highly cited publications across the research literature (and within most subfields) are more likely to be characterized as HC and HN than less highly cited publications.  Key to Uzzi is their random graph model, where  a reference cited in a publication is randomly replaced by another article from the same year as the cited reference, thus producing a random assignment of references to each paper. The model treats potential substitutions as equi-probable, irrespective of disciplinary origin. Accordingly, we hypothesize that analyzing semantically related sets of documents (and limiting substitutions to the citations in the local network) will reduce model misspecification and better simulate citation practice, leading to different and more relevant conclusions.  
We developed a highly efficient algorithm to simulate under a refined random graph model. Our study on three semantically-themed citation networks reveals significantly different patterns of conventionality and novelty between  citation networks and disciplines.

@@

\bibliography{cocit_r}
